\Large Generative Dynamics of Supreme Court Citations: \\ Analysis with a New Statistical Model

### 2020-05-04 Tex/paper.tex
completed dependence terms

% Activity
In order to account for the activity effect, the straightforward thing to do is to add the \textit{geometrically weighted outdegree} (gwodegree) statistic, which is defined as gwidegree with the difference that $D_r(C_t, C_{<t})$ represents the number of nodes with outdegree $r$. However, adding the gwodegree statistic causes the model to degenerate again. We circumvent degeneracy by adding the outdegree of every node that entered the network prior time $t$ as a receiver effect. In other words, this statistic adds up the outdegree of cases that are being cited at time $t$ and examines whether cases that show a high degree of activity are being more likely to be cited in the future.

@@

\subsection{Predictive Performance}

>>>>

% Activity
We include one more structural network effect to adjust for inherent differences across cases in terms of the overall scope of the legal issues addressed in a case.  \citet{fowler2008authority} finds that cases vary in the degree to which they serve as ``hubs''---citing to many other cases. We expect that new cases will be more likely to cite cases that themselves cited many cases, because cases that themselves cite a large number of cases address a broader array of legal issues. We include the outdegree of every node that entered the network prior time $t$ as a receiver effect. We expect the coefficient on this term to be positive. This is not technically a dependence term, as it is formulated as a covariate, but we discuss it in the current section because it is purely a network structure effect.

@@

\subsection{Model Fit}
